\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage{ifthen}
\usepackage{ifpdf}
\usepackage{color}
\usepackage{lmodern}
\usepackage{marvosym}
\usepackage{url}
% \usepackage{hyperref}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{ragged2e}
\usepackage[scale=0.915]{geometry}
\usepackage{import}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}

\name{Luiz Berilo}{Casemiro Queiroz}
\newcommand*{\customcventry}[7][.13em]{
\begin{tabular}{@{}l}
{\bfseries #4} \
{\itshape #3}
\end{tabular}
\hfill
\begin{tabular}{l@{}}
{\bfseries #5} \
{\itshape #2}
\end{tabular}
\ifx&#7&%
\else{\
\begin{minipage}{\maincolumnwidth}%
\small#7%
\end{minipage}}\fi%
\par\addvspace{#1}}
\begin{document}
\makecvtitle
\vspace*{-16mm}
\begin{center}\textbf{Backend Software Engineer}\end{center}

\section{Contact}{
  \begin{center}
	  \faMobile\enspace +55 85 989071945                                                                  & \enspace berilo.queiroz@gmail.com & \enspace\faHome\enspace Fortaleza, BR \\
	  \faLinkedin\enspace \color{blue} \href{https://www.linkedin.com/in/beriloqueiroz}{in/beriloqueiroz} &
	  \faGithub\enspace \color{blue} \href{https://github.com/beriloqueiroz}{github.com/beriloqueiroz}    & \enspace
  \end{center}
 }

\section{Profile}
 {
  Results-driven professional with a strong background in developing and maintaining software solutions. Adept at troubleshooting and resolving software issues to ensure the stability and performance of products. Skilled in designing and developing applications with a focus on scalability and security.
 }

\section{Skills}
 {
  Java Springboot, Go/Golang, Javascript, NodeJs, typescript, C\# .NET, HTML, CSS \\
  MySQL, PostgreSQL, MongoDB, \\
  RESTful API, Testing, gRPC, Microservices, Docker\\
  SOLID, Clean Architecture, Git, DDD \\
  Scrum, Kanban\\
  Kubernetes, AWS Ec2 RDS, Google Cloud Run\\
  Teamwork, Communication, Problem Analysis, Business Vision, Commitment\\
 }

\section{Professional Experience}

\vspace{\baselineskip}

\begin{samepage}
	\customcventry{03/2023 - Present}{{\color{blue}\href{https://www.buson.com/}{Buson}}}%
	{FullStack Developer II}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item FullStack development using HTML, CSS, Javascript, Nodejs, Typescript, VueJs, Svelte, Handlebars, Java, Spring Boot.
			\item Working in the e-commerce squad, operating deployment procedures, fixing build errors in Jenkins and Argos, and deploying to production using Kubernetes.
			\item Actively participates and contributes to understanding the complexity of new features, as well as making technical decisions.
			\item Contributed to the delivery of several features that positively impact the company's revenue and independence.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{05/2022 - 02/2023}{{\color{blue}\href{https://www.buson.com/}{Buson}}}%
	{FullStack Developer}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item FullStack development using HTML, CSS, Javascript, Nodejs, Typescript, VueJs, Svelte (POC), Handlebars, Java, Spring Boot.
			\item Worked in the POS and e-commerce squad.
			\item Contributed to more than one feature focused on user experience (B2B).
			\item Contributed to more than 10 features focused on user experience (B2C).
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{01/2021 - 04/2022}{{\color{blue}\href{https://www.maquiadoro.com/}{Maquiadoro}}}%
	{FullStack Developer and Director}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Backend development in NodeJs, Typescript, focusing on SOLID principles and clean architecture.
			\item Used Docker, MongoDB, Postgres, and MySQL.
			\item Frontend work in ReactJs on some projects. Maintenance of the e-commerce frontend.
			\item Technology consulting and IT team leadership, applying agile SCRUM methodology.
			\item Technology consulting and directing the IT team, applying agile SCRUM methodology.
			\item Contributed to greater technological independence in ERP integration and e-commerce platform, developing an integration hub.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{05/2019 - 12/2020}{{\color{blue}\href{https://www.maquiadoro.com/}{Maquiadoro}}}%
	{PO/Developer and Director}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Acted as Product Owner and developer in the IT team, applying agile SCRUM methodology.
			\item Developed microsystems for process management and automation.
			\item Technology consulting and IT team leadership.
			\item Contributed to greater technological independence in financial management, assisting in building a financial management system.
			\item Fostered tax and fiscal understanding with constant training.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{08/2018 - 01/2019}{{\color{blue}\href{https://www.maquiadoro.com/}{Maquiadoro}}}%
	{E-commerce and Operations Director}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Responsible for data analysis and metrics, setting goals based on strategic planning.
			\item Process mapping, fiscal and tax analysis.
			\item Business metrics monitoring.
			\item Contributed to the conception and project of a concept store, aligned with omnichannel strategy.
			\item Expanded the company's operational capacity by more than 20\%, actively participating in strategic definition and goal setting, enabling more analytical management.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{07/2016 - 07/2018}{{\color{blue}\href{https://www.maquiadoro.com/}{Maquiadoro}}}%
	{Commercial Director and Logistics/Shipping Director}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Expanded logistics and managed the commercial sector.
			\item Sales analysis, procurement team management, fiscal and tax analysis.
			\item Process automation and company modernization.
			\item Reduced operational costs by more than 30\% through logistics process optimization and improved stakeholder relations.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{09/2015 - 06/2016}{{\color{blue}\href{https://www.nexoengenharia.com/}{Nexo Engenharia}}}%
	{Mechatronics Engineer}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Developed and executed projects in building and industrial automation.
			\item Developed programs for Programmable Logic Controller (PLC) and automation systems.
			\item Supervisory software configuration.
			\item Contribution to projects: Participated in commissioning, programming of people counting systems, water measurement, energy measurement, SDAI, and large-scale building climate control systems.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{01/2015 - 09/2015}{{\color{blue}\href{https://www.nexoengenharia.com/}{Nexo Engenharia}}}%
	{Automation Systems Analyst}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Developed programs for Programmable Logic Controller (PLC) and automation systems.
			\item Supervisory software configuration.
			\item Participation in building and industrial automation projects.
			\item Project contributions: Actively participated in more than 4 automation and SDAI projects, contributing to successful implementation and system startup.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{06/2014 - 01/2015}{{\color{blue}\href{https://www.nexoengenharia.com/}{Nexo Engenharia}}}%
	{Automation Assistant}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Developed programs for Programmable Logic Controller (PLC) and automation systems.
			\item Supervisory software configuration.
			\item Automation system start-up.
			\item Learning and contribution: Acquired practical knowledge in automation and contributed to project.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{12/2012 - 06/2014}{{\color{blue}\href{https://www.nexoengenharia.com/}{Nexo Engenharia}}}%
	{Intern}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Developed programs for Programmable Logic Controller (PLC) and automation systems.
			\item Supervisory software configuration.
			\item Quantity surveying and project points documentation.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{2012 - 2014}{{\color{blue}\href{https://www.ifce.edu.br/}{Laboratório de Processamento de Energia - LPE (IFCE)}}}%
	{Scholarship Holder}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Development of projects in the field of power electronics, control, and wind energy.
			\item Research and development: Contributed to 2 research projects, resulting in academic publications.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\customcventry{11/2011 - 05/2012}{{\color{blue}\href{https://www.tsautomacao.com.br/}{TS Tecnologia e soluções em automação industrial LTDA}}}%
	{Intern}{---}{---}{%
		\begin{itemize}[leftmargin=0.6cm, label={\textbullet}]
			\item Analysis of industrial automation systems.
			\item Programming of Programmable Logic Controllers (PLCs).
			\item Efficient implementation: Participated in the implementation of 2 industrial automation systems, improving process efficiency in the oil and gas sector.
		\end{itemize}
	}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\section{Courses \& Certifications}
	 {\begin{itemize}[label=\textbullet]
		  \item Clean Architecture module (2023) - \underline{\color{blue}\href{https://fullcycle.com}{FullCycle}}
		  \item Hexagonal Architecture module (2023) - \underline{\color{blue}\href{https://fullcycle.com}{FullCycle}}
		  \item Web Application Security (2023) - \underline{\color{blue}\href{https://udemy.com}{Udemy}}
		  \item Event Storming module (2022) - \underline{\color{blue}\href{https://fullcycle.com}{FullCycle}}
		  \item Communication between systems module (2022) - \underline{\color{blue}\href{https://fullcycle.com}{FullCycle}}
		  \item Domain-Driven Design (DDD) module (2022) - \underline{\color{blue}\href{https://fullcycle.com}{FullCycle}}
		  \item SOLID Express module (2022) - \underline{\color{blue}\href{https://fullcycle.com}{FullCycle}}
		  \item Software Architecture Fundamentals module (2022) - \underline{\color{blue}\href{https://fullcycle.com}{FullCycle}}
		  \item Docker module (2022) - \underline{\color{blue}\href{https://fullcycle.com}{FullCycle}}
		  \item HTML, CSS, Javascript (2021-2022) - \underline{\color{blue}\href{https://rocketseat.com.br}{Rocketseat}}
		  \item Node.js, TypeScript, RESTful API (Express) (2021-2022) - \underline{\color{blue}\href{https://rocketseat.com.br}{Rocketseat - ignite}}
		  \item React (2021-2022) - \underline{\color{blue}\href{https://rocketseat.com.br}{Rocketseat - ignite}}
		  \item HTML - Basic Training (2020-2021) - \underline{\color{blue}\href{https://linkedin.com/learning}{LinkedIn Learning}}
		  \item Project Budget Management (2020-2021) - \underline{\color{blue}\href{https://linkedin.com/learning}{LinkedIn Learning}}
		  \item Project Schedule Management (2020-2021) - \underline{\color{blue}\href{https://linkedin.com/learning}{LinkedIn Learning}}
		  \item Industry 4.0: Fundamentals of the Fourth Industrial Revolution (2020-2021) - \underline{\color{blue}\href{https://linkedin.com/learning}{LinkedIn Learning}}
		  \item Fundamentals of Artificial Intelligence: Machine Learning (2020-2021) - \underline{\color{blue}\href{https://linkedin.com/learning}{LinkedIn Learning}}
		  \item Remote Software Development (2020-2021) - \underline{\color{blue}\href{https://linkedin.com/learning}{LinkedIn Learning}}
		  \item III Consultant Training Program (2020-2021) - \underline{\color{blue}\href{https://domani.com.br}{DOMANI}}
		  \item Elipse E3 Developers (2015) - \underline{\color{blue}\href{https://elipse.com}{Elipse Software}}
		  \item Short Course in Configuration and Project Development of CCTV (2015) - \underline{\color{blue}\href{https://axis.com}{Axis Communications}}
		  \item Java SE (2010) - \underline{\color{blue}\href{https://cpqt.com.br}{Centro de Pesquisa e Qualificação Tecnológica}}
	  \end{itemize}}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\section{Education}
	\customcventry{2023-2024}{{\color{blue}\href{https://fctech.edu.br}{FullCycle Technology College}}}{Postgraduate (Go Language)}{---}{}{}
	\customcventry{2020-2021}{{\color{blue}\href{https://www.ipog.edu.br}{IPOG}}}{Postgraduate - MBA in Project and Process Management}{---}{}{}
	\customcventry{2008-2015}{{\color{blue}\href{https://ifce.edu.br}{IFCE, Brazil}}}{Bachelor's Degree - Mechatronics Engineering}{---}{}{}
\end{samepage}
\vspace{\baselineskip}

\begin{samepage}
	\section{Languages}
	\begin{multicols}{2}
		\begin{itemize}[label=\textbullet]
			\item \textbf{English} [Intermediate]
			\item \textbf{Portuguese} [Native]
		\end{itemize}
	\end{multicols}
\end{samepage}
\vspace{\baselineskip}

\end{document}
